---
name: Jason S.
surname: Tsukahara
position: "PhD Student"
address: "School of Psychology, Georgia Institute of Technology"
www: englelab.gatech.edu/jason
email: "jason.tsukahara@gatech.edu"
googlescholar: "393wE14AAAAJ"
twitter: jasontsukahara
headcolor: 414141 # use black color
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    keep_tex: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae);library(tibble)
```


# Education

```{r}
tribble(
  ~ Degree,
  ~ Advisor,
  ~ Year,
  ~ Institution,
  ~ Where,
  "Doctor of Philosophy, Cognition and Brain Science",
  "Advisor: Randall Engle, Ph.D.",
  "2014-Present",
  "Georgia Institute of Technology",
  "Atlanta, GA, USA",
  "Master of Art, General Experimental Psychology",
  "Advisor: Hideya Koshino, Ph.D.",
  "2014",
  "California State University San Bernardino",
  "San Bernardino, CA, USA",
  "Bachelor of Art, Behavioral Neuroscience",
  NA,
  "2011",
  "Western Washington University",
  "Bellingham, WA, USA",
) %>%
  detailed_entries(
    with = Degree,
    where = Year,
    what = Institution,
    when = Where,
    why = Advisor
  )
```

# Research Interests

My research is primarily concerned with understanding the nature of attention control. My education and experience of working in different research labs has allowed me to approach the study of attention control from various perspectives; experimental, individual differences, and neuroscience. My research interests include but are not limited to:

* The nature of individual differences in attention control
* Tracking the focus of attention with pupillometry and mind wandering reports 
* The role of the locus coeruleus norepinephrine system in attention control
* The role of functional connectivity within and between brain networks to individual differences in attention control and higher-order cognitive abilities
* The possibility of training attention

# Submitted Articles and Preprints

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
\setlength{\baselineskip}{0.2in}

**Tsukahara**, J.S., & Engle, R.W. (2020). Is baseline pupil size related to cognitive ability? Yes (under proper lighting conditions). Submitted to *Cognition*. https://doi.org/10.31234/osf.io/pvz24. **Citations: `r rcrossref::cr_citation_count("10.31234/osf.io/pvz24")$count`**

**Tsukahara**, J.S., & Engle, R.W. (2020). The locus coeruleus-norepinephrine system and fluid intelligence. *PsyArXiv*: https://doi.org/10.31234/osf.io/eg3vw. **Citations: `r rcrossref::cr_citation_count("10.31234/osf.io/eg3vw")$count`**

\endgroup

# Journal Articles

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
\setlength{\baselineskip}{0.2in}

Borges, U., Pfannenstiel, M., **Tsukahara**, J., Laborde, S., Klatt, S., & Raab, M. (2021). Transcutaneous vagus nerve stimulation via tragus or cymba conchae : Are its psychophysiological effects dependent on the stimulation area? *International Journal of Psychophysiology, 161*, 64–75. https://doi.org/10.1016/j.ijpsycho.2021.01.003. **Citations: `r rcrossref::cr_citation_count("10.1016/j.ijpsycho.2021.01.003")$count`**

Martin, J., **Tsukahara**, J.S., Draheim, C., Shipstead, Z., Mashburn, C., Vogel, E.K., & Engle, R.W. (2020). The visual arrays task: Visual storage capacity or attention control?. *In Press at Journal of Experimental Psychology: General.*

Burgoyne, A.P., **Tsukahara**, J.S., Draheim, C., Engle, R.W. (2020). Differential and experimental approaches to studying intelligence in humans and non-human animals. Learning and Motivation. https://doi.org/10.1177/0963721420969371. **Citations: `r rcrossref::cr_citation_count("10.1177/0963721420969371")$count`**

Draheim, C., **Tsukahara**, J.S., Martin, J.D., & Engle, R.W. (2020). A toolbox approach to improving the measurement of attention control. *Journal of Experimental Psychology: General*. https://doi.org/10.1037/xge0000783. **Citations: `r rcrossref::cr_citation_count("10.1037/xge0000783")$count`**

**Tsukahara**, J.S., Harrison, T.L., Draheim, C., Martin, J., & Engle, R.W. (2020). Attention control: The missing link between sensory discrimination and intelligence. *Attention, Perception, & Psychophysics*. https://doi.org/10.3758/s13414-020-02044-9. **Citations: `r rcrossref::cr_citation_count("10.3758/s13414-020-02044-9")$count`**

**Tsukahara**, J.S., Harrison, T.L., & Engle, R.W. (2016). The relationship between baseline pupil size and intelligence. *Cognitive Psychology*, 91, 109-123. http://dx.doi.org/10.1016/j.cogpsych.2016.10.001. **Citations: `r rcrossref::cr_citation_count("10.1016/j.cogpsych.2016.10.001")$count`**

\endgroup

# Chapters

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
\setlength{\baselineskip}{0.2in}

Mashburn, C.A., **Tsukahara**, J.S., Draheim, C., & Engle, R.W. (2020). Individual differences in attention control: Implications for the relationship between working memory capacity and fluid intelligence. In R.H. Logie, V. Camos, & N. Cowan (Eds.), *Working memory: The state of the science.* Oxford University Press.

\endgroup

# Professional Presentations

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
\setlength{\baselineskip}{0.2in}

**Tsukahara**, J.S., & Engle, R.W. (2019). Individual differences in baseline pupil size: Why lighting conditions matter. **Poster** presented at the 60th Annual meetings of the Psychonomic Society, Montréal, Canada. https://osf.io/7fntm/

Draheim, C., **Tsukahara, J. S.**, Martin, J. D., Mashburn, C. A., & Engle, R. W. (2019). Attention control is a unitary concept when measured with accuracy-based tasks. **Poster** presented at the 60th annual meeting of the Psychonomic Society, Montréal, Canada.

Draheim, C., Martin, J. D., **Tsukahara**, J.S., Mashburn, C. A., & Engle, R. W. *Measurement of Attention Control* **Paper** presented at the 59th meeting of the Psychonomic Society, New Orleans, LA.

**Tsukahara**, J.S., & Engle, R.W. (2018). Pupil size as an indicator of arousal and task focus. **Poster** presented at the 59th Annual meetings of the Psychonomic Society, New Orleans, LA.

**Tsukahara**, J.S., Harrison, T. L., Hicks, K. L., Draheim, C., Martin, J. D., & Engle, R. W. (November 2017). *Measuring attention control: Can we do better?* **Poster** presented at the 58th annual meeting of the Psychonomic Society, Vancouver, Canada.

Harrison, T. L., Hicks, K. L., Draheim, C., **Tsukahara**, J.S., & Engle, R. W. (November, 2016). *Sensory discrimination, working memory, and fluid intelligence.* **Paper** presented by Engle, R.W. at the 57th annual meeting of the Psychonomic Society, Boston, MA.

**Tsukahara**, J.S., & Engle, R.W. (November, 2016). *Mind wandering in low and high demanding tasks: Frequency vs. degree of disengagement.* **Poster** presented at the 57th annual meeting of the Psychonomic Society, Boston, MA.

**Tsukahara**, J.S., Harrison T.L. & Engle, R.W. (2016). *More than meets the eye: Converging evidence from pupillometry, locus coeruleus function, and resting-state functional connectivity.* **Paper** presented by Tsukahara, J.S. at the North Georgia Regional Memory Meeting, Atlanta, GA.

**Tsukahara**, J.S., Harrison, T.L., & Engle, R.W. (April, 2016). *More than meets the eye: The relationship between pupil size and intelligence.* **Poster** presented at the Callosum Conference.

**Tsukahara**, J.S., Harrison, T.L., & Engle, R.W. (2015). *The eyes have it: The relationship between pupil size and intelligence.* **Paper** presented by Engle, R.W. at the 56th annual meeting of the Psychonomic Society, Chicago, IL.

**Tsukahara**, J.S., & Koshino, H. (November, 2014). *Does working memory capacity have the same effect on the Simon task as working memory load?* **Poster** presented at the 55th annual meeting of the Psychonomic Society, Long Beach, CA.

Koshino, H., Veltri, G.A., **Tsukahara**, J.S., Alderson, E. (November, 2014). *Effects of working memory and perceptual load on Simon interference.* **Poster** presented at the 55th annual meeting of the Psychonomic Society, Long Beach, CA.

**Tsukahara**, J.S. (2014, June). *The effect of working memory capacity and working memory load on the Simon task.* **Paper** presented at the 1st annual Learning Research Institute conference, California State University, San Bernardino, CA.

**Tsukahara**, J.S. (2014, June). *Perceptual load effect in the Simon task.* **Paper** presented at the 3rd annual student Research Symposium “Meeting of the Minds”, California State University, San Bernardino, CA.

**Tsukahara**, J.S., Rivera, L., & Koshino, H. (April, 2014). *The effects of perceptual load on a Simon task.* **Poster** presented at the 94th annual Western Psychological Association convention, Portland, OR.

Koshino, H., **Tsukahara**, J.S., Rivera, L. Veltri, G.A., Cross, T., Alderson, E. (April, 2014). *Effects of perceptual load and working memory on a Simon task.* **Poster** presented at the 94th annual Western Psychological Association convention, Portland, OR.

Koshino, H. & **Tsukahara**, J.S. (November, 2013). *Relative effectiveness of attention capture between color singleton and working memory.* **Poster** session presented at the 54th annual meeting of the Psychonomic society, Toronto, Canada.

**Tsukahara**, J.S., Banerjee, S., & Koshino, H. (April, 2013). *Interaction between Simon and Flanker effects.* **Poster** session presented at the 93rd annual Western Psychological Association convention, Reno, NV.

\endgroup


# Teaching Experience

## Primary Instructor

```{r}
tribble(
  ~ Year,
  ~ Where,
  ~ Name,
  ~ Duty,
  'Spring 2019',
  "Georgia Institute of Technology",
  "PSYC 6020: Graduate Level Statistics II Lab",
  "Taught regression and general linear model in R and SPSS; Course design; weekly labs; office hours",
  'Spring 2013 - Spring 2014',
  "California State University",
  "Intro to Experimental Psychology Lab Section",
  "Taught regression and general linear model in R and SPSS; Course design; weekly labs; office hours"
) %>%
  detailed_entries(when = Year,
                   where = Where,
                   with = Name,
                   what = Duty) 
```

## Seconday Instructor

```{r}
tribble(
  ~ Year,
  ~ Where,
  ~ Name,
  ~ Duty,
  'Fall 2016',
  "Georgia Institute of Technology",
  "Introduction to Psychology",
  "Teaching practicum; Guest Lecture: Research Methodology, Attention and Consciousness, Thinking and Intelligence",
  'Fall 2017',
  "Georgia Institute of Technology",
  "Guest Lecture: Introduction to I/O Psychology",
  "Lectured on an introduction to research on intelligence",
  'Winter 2013 - Spring 2013',
  "California State University",
  "Supplemental Instructions to Psychological Statistics",
  "Provided additional instruction in undergraduate level statistics"
) %>%
  detailed_entries(when = Year,
                   where = Where,
                   with = Name,
                   what = Duty,) 
```


# Open-Source Software and Website Management

## R Packages

```{r}
tribble(
  ~ Name,
  ~ What,
  ~ Link,
  "pupillometry",
  "An R package to preprocess pupil data",
  "https://dr-jt.github.io/pupillometry",
  "semoutput",
  "An R package to create nice looking output for CFA and SEM analysis using lavaan and semPlot",
  "https://dr-jt.github.io/semoutput",
  "englelab",
  "An R package for processing complex-span and attention control tasks downloaded from the EngleLab",
  "https://englelab.github.io/englelab/"
) %>%
  detailed_entries(with = Name,
                   what = What,
                   where = Link)
```

## Website Management

```{r}
tribble(
  ~ Name,
  ~ What,
  ~ Link,
  "Attention and Working Memory Lab Website",
  "Design and Manage Lab Website",
  "https://englelab.gatech.edu"
) %>%
  detailed_entries(with = Name,
                   what = What,
                   where = Link)
```


# Technical Skills

## **Research Methods**

*My primary experience is in design of research experiments using both individual differences and experimental approaches, as well as designing experiments to measure baseline and task-evoked changes in pupil size.*

Individual differences \hfill Functional magnetic resonance imaging (*fMRI*)

Experimental manipulation \hfill Electroencephalography (*EEG*)

Pupillometry
    
## **Statistical Methods**

General linear model (*Regression, ANOVA*) \hfill Structural equation modelling

Factor analysis (*Pricipal components, Exploratory factor analysis*) \hfill Multilevel modelling

## **Programming**

*My primary programming experience is in creating experimental tasks, data management and processing, statistical analysis, and website design.*

**Experimental Tasks** \hfill __Data Management and Analysis__

E-Prime \hfill R (*see open-source software section*)

PsychoPy \hfill SPSS (*statistical analysis tool*)

**Website and Graphic Design**

HTML; CSS

Adobe Illustrator; Adobe Lightroom


# Graduate Coursework

Cognitive Psychology \hfill Statistical Analysis I (*ANOVA*)

Intelligence (*seminar*) \hfill Statistical Analysis II (*regression*)

Neuroimaging (*seminar*) \hfill Multivariate Statistics

Life-Span Deveolpmental Psychology \hfill Psychometric Theory

Biopsychology \hfill Structural Equation Modeling

Transcranial Magnetic Stimulation (*seminar*) \hfill Psychological
Testing

Teaching Practicum \hfill Research Methods

Learning and Motivation

Personal and Social Psychology


# Professional Service

**Peer-reviewed for**:

*Psychonomic Bulletin and Review*

*Journal of Experimental Psychology: Learning, Memory, and Cognition*

*Attention, Perception, and Psychophysics*

*Biological Psychology*

*Cognitive, Affective, and Behavioral Neuroscience*

*Cognition*

*Journal of Experimental Psychology: General*

*Current Directions in Psychological Science*

*Attention, Perception, and Psychophysics*

